Learning constraints in spreadsheets and tabular data

### 2016-09-23 Paper/ECAI/tabular.tex
Formatting

Our proposed methodology contains the following steps:
\begin{enumerate}
\item Extract headerless tables from tabular data
\item Partition the tables into contiguous, type-consistent \textit{superblocks}
\item Generate for each constraint template all valid argument assignments in two steps:
\begin{enumerate}
\item For each constraint template~$s$, generate all assignments $(\sbl{1}, \ldots ,\sbl{n})$ where each~$\sbl{i}$ is a superblock and the~$\sbl{i}$ are \textit{compatible} (defined below) with the signature of~$s$. 
\item For each generated assignment $(\sbl{1}, \ldots ,\sbl{n})$ in 3a), find all valid constraints $s(\ssbl{1}, \ldots, \ssbl{n})$ such that for all $i$ holds $\ssbl{i} \sqsubseteq \sbl{i}$ and the signature and definition of~$s$ are satisfied.
\end{enumerate}
\end{enumerate}

>>>>

Our proposed methodology contains the following steps:
\begin{enumerate}
\item Extract headerless tables from tabular data
\item Partition the tables into contiguous, type-consistent \textit{superblocks}
\item Generate for each constraint template all valid argument assignments in two steps:
\begin{enumerate}
\item For each constraint template~$s$, generate all assignments $(\sbl{1}, \ldots ,\sbl{n})$ where each~$\sbl{i}$ is a superblock and the~$\sbl{i}$ are \textit{compatible} (defined below) with the signature of~$s$. 
\item For each assignment $(\sbl{1}, \ldots ,\sbl{n})$ generated in 3a), find all constraints $s(\ssbl{1}, \ldots, \ssbl{n})$ such that for all $i$ holds $\ssbl{i} \sqsubseteq \sbl{i}$ and the signature and definition of~$s$ are satisfied.
\end{enumerate}
\end{enumerate}
